Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond

### 2024-01-04 main.tex
:pencil: Add background

\begin{document}
\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
		Yijie~Mao,~\IEEEmembership{Member,~IEEE,}
		Shanpu~Shen,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	% \thanks{
	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	% 	B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	% }
}
\maketitle

% \begin{abstract}
% \end{abstract}

% \begin{IEEEkeywords}
% \end{IEEEkeywords}

@@

>>>>

\begin{document}
\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
		Massimo~Franceschetti,~\IEEEmembership{Fellow,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	% \thanks{
	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	% 	B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	% }
}
\maketitle

\begin{abstract}
	\gls{ris} is a promising technology that recycles and redistributes ambient waves for improved wireless performance.
	% \gls{ris} is a real-time programmable reflector that recycles and redistributes ambient waves for improved wireless performance.
	This paper investigates the use of passive \gls{ris} for channel shaping in \gls{mimo} \gls{pc} and \gls{ic}.
	We depart from the widely-adapted diagonal phase shift model and focus on a general asymmetric \gls{bd} architecture, which allows off-diagonal entries by in-group connections between elements.
	For arbitrary group size, we propose a closed-form iterative algorithm for quadratic problems and a \gls{rcg} algorithm for general problems.
	Various case studies are then conducted, including rate maximization and Pareto singular value characterization for \gls{pc}, and interference alignment and \gls{wsr} maximization for \gls{ic}.
	To quantify channel shaping capability, we also derive analytical bounds under specific scenarios and validate those by aforementioned methods.
	Simulation results suggest the advantage of \gls{bd} \gls{ris} scales with group size, while dyadic or tetradic architecture usually strikes a good balance between performance and complexity.
	% Through theoretical analysis and numerical evaluation,
	Our findings unlock unprecedented efficiency and adaptability, paving the way for smarter and greener wireless environments.
	% truly programmable
	% useful guidelines for prototype design.
\end{abstract}

\begin{IEEEkeywords}
	Reconfigurable intelligent surface, channel shaping, point-to-point channel, interference channel.
\end{IEEEkeywords}

@@

\begin{section}{Introduction}
	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of low-power reflecting elements.
	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than conventional relays.
	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication, backscatter, sensing, and power transfer literature \cite{Wu2019,Wu2020c,Yang2020,Zheng2021,Jia2020,Liang2022,Liu2022a,Hua2023,Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
	Although fruitful outcomes have been harvested by fancy optimization tools, one fundamental yet critical unanswered question is the \emph{channel shaping} capability of \gls{ris}: To what extent can \gls{ris} reshape the wireless channel?

	% we aim to answer this question by a simple yet insightful approach: \emph{from diagonal to beyond}.
	% The answer depends heavily on the phase shift model of \gls{ris}.
	Before answering the question, we first need to revisit the \gls{ris} architecture.

	% Despite the fruitful results, the existing literature on \gls{ris} is still limited to the diagonal phase shift model, where the phase shifters are constrained to be diagonal matrices.

	% \gls{ris} also offers a new degree of freedom for \emph{channel shaping}, i.e., to reshape the wireless channel to a desired form.
\end{section}
